### 2021-06-25 chapters/3_background.tex

\section{Neural networks for clustering}
There are many different types of neural networks.
These neural networks have different applications based on their properties.
For this thesis we will focus on neural networks designed for clustering.
\newline
Neural networks consists of machine learning algorithms\cite{supervisedUnsupervised}. 
These machine learning algorithms are divided in supervised and unsupervised learning algorithms\cite{supervisedUnsupervised}.
Supervised machine learning algorithms are commonly used for classification and categorization\cite{supervisedUnsupervised}.
Unsupervised machine learning algorithms are commonly used for clustering and dimensionality reduction\cite{supervisedUnsupervised}.
\newline
K.L. Du surveyed different neural networks and algorithms used for clustering:
\begin{itemize}
    \item Self organizing map.
    \item Learning vector quantization.
    \item C-means clustering.
    \item Mountain and Substractive clustering.
    \item Neural gas.
    \item ART networks.
    \item Fuzzy c-means.
\end{itemize}
In his paper he also touches on subjects relevant to clustering and neural networks such as the under-utilization problem, fuzzy clustering, robust clustering, clustering based on non- Euclidean distance measures, supervised clustering, and hierarchical clustering.
Neural network variants and their references are also discussed.
\newline
K.L. Du describes the mathematical principles on which the neural networks and algorithms are based.
He closes his paper with computer simulations of some of the neural networks he surveyed.

>>>>

\section{Neural networks for clustering}
\label{ch:neuralNetworkSurvey}
There are many different types of neural networks.
These neural networks have different applications based on their properties.
For this thesis we will focus on neural networks designed for clustering.
\newline
Neural networks consists of machine learning algorithms\cite{supervisedUnsupervised}. 
These machine learning algorithms are divided in supervised and unsupervised learning algorithms\cite{supervisedUnsupervised}.
Supervised machine learning algorithms are commonly used for classification and categorization\cite{supervisedUnsupervised}.
Unsupervised machine learning algorithms are commonly used for clustering and dimensionality reduction\cite{supervisedUnsupervised}.
\newline
K.L. Du surveyed different neural networks and algorithms used for clustering\cite{Du2010Clustering:Approach}:
\begin{itemize}
    \item Self organizing map.
    \item Learning vector quantization.
    \item C-means clustering.
    \item Mountain clustering.
    \item Neural gas.
    \item ART networks.
    \item Fuzzy c-means.
\end{itemize}
In his paper he also touches on subjects relevant to clustering and neural networks such as the under-utilization problem, fuzzy clustering, robust clustering, clustering based on non- Euclidean distance measures, supervised clustering, and hierarchical clustering.
Neural network variants and their references are also discussed.
\newline
K.L. Du describes the mathematical principles on which the neural networks and algorithms are based.
He closes his paper with computer simulations of some of the neural networks he surveyed.

### 2021-06-25 chapters/rq2/1_experiment_design.tex

\documentclass[../main]{subfiles}
\begin{document}
% Because we use sections but these sections should be interpreted as chapters for rq1 and rq2 sectioning.
\clearpage
\section{Experiment design}
In this chapter we will design an experiment to answer our second research question.
HYOPTHESIS HERE\todo{do hypothesis}
Our goal is to achieve a mutation score that is as close as possible to the mutation score of a full set of executed mutants.
\newline
\toto{finish this}

\subsection{Selecting a neural network}

>>>>

\documentclass[../../main]{subfiles}
\begin{document}
% Because we use sections but these sections should be interpreted as chapters for rq1 and rq2 sectioning.
\clearpage
\section{Experiment design}
In this chapter we will design an experiment to answer our second research question.
HYOPTHESIS HERE\todo{do hypothesis}
Our goal is to achieve a mutation score that is as close as possible to the mutation score of a full set of executed mutants.
\newline
\todo{finish this}

\subsection{Selecting a neural network}
Our starting point for selecting a neural network is the survey done by K.L. Du\cite{Du2010Clustering:Approach}.
We start with a process of elimination to filter the neural networks named in chapter \ref{ch:background}.
\newline
supervised networkd\todo{elaborate why no supervised}
\newline
The moutain clustering networks is effective method for estimating the number of clusters\cite{Du2010Clustering:Approach}. 
The goal of this experiment is to cluster mutants, while finding out the number of clusters we need might be valuable it is not what we want to achieve. Therefore we will not select mountain clustering.
Subtractive clustering is a modified form of mountain c\cite{Du2010Clustering:Approach}. 
\newline

\subsection{Training method}

\subsection{Validation}
